\Trill: Secure firewall-traversing networking

### 2012-12-14 6.858/paper/paper.tex
Moar formatting

\subsection{Security}
The security of our system is based on standard cryptographic infrastructure and
libraries. By ``identities,'' we mean public key pairs, the private half of
which is uniquely known by an individual. This identity can be given one or more
names by means of X.509 certificates, and standard mechanisms like TLS allow
owners of identities to securely establish a communication channel and mutually
verify the other's identity.

\section*{Federated Identity}
As with other federated protocols like XMPP and email, \Trill handles are based
on DNS. In particular, \Trill's handles use RFC 2822's \verb`addr-spec`
specification, in which every \verb`domain` is allowed complete control over the
\Trill handles given out as \verb`local-part`'s at their domain. Domains wishing
to run \Trill must also publish information about its \Trill servers using DNS
SRV records.

@@

\section*{Establishing Trust}
Trust in \Trill is established between two clients when each of them verifies
that the other client's certificate is signed by the other client's domain key.
However, the clients must also recursively verify this key, to make sure the
purported domain key was actually issued by the controller of the domain name.

@@

\subsection{Firewall Traversal}
Due to restrictions on many firewalls and NATs in place on the Internet, it is
impossible for arbitrary clients on the internet to establish peer-to-peer
communication. There are techniques for firewall/NAT traversal which involve
``tricking'' the networking layer into establishing a connection. We implemented
something similar to \texttt{chownat} (\url{http://samy.pl/chownat/}) in \Trill,
which appears to be a standard way to do this.

>>>>

\subsection{Security}

The security of our system is based on standard cryptographic infrastructure and
libraries. By ``identities,'' we mean public key pairs, the private half of
which is uniquely known by an individual. This identity can be given one or more
names by means of X.509 certificates, and standard mechanisms like TLS allow
owners of identities to securely establish a communication channel and mutually
verify the other's identity.

\subsection{Federated Identity}

As with other federated protocols like XMPP and email, \Trill handles are based
on DNS. In particular, \Trill's handles use RFC 2822's \verb`addr-spec`
specification, in which every \verb`domain` is allowed complete control over the
\Trill handles given out as \verb`local-part`'s at their domain. Domains wishing
to run \Trill must also publish information about its \Trill servers using DNS
SRV records.

@@

\subsection{Establishing Trust}

Trust in \Trill is established between two clients when each of them verifies
that the other client's certificate is signed by the other client's domain key.
However, the clients must also recursively verify this key, to make sure the
purported domain key was actually issued by the controller of the domain name.

@@

\subsection{Firewall Traversal}

Due to restrictions on many firewalls and NATs in place on the Internet, it is
impossible for arbitrary clients on the internet to establish peer-to-peer
communication. There are techniques for firewall/NAT traversal which involve
``tricking'' the networking layer into establishing a connection. We implemented
something similar to \texttt{chownat} (\url{http://samy.pl/chownat/}) in \Trill,
which appears to be a standard way to do this.
